HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-05-31 paper/main.tex
emnlp format
Added the correlation graphs

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

@@

\def\perscite#1{\citet{#1}}
\def\parcite#1{\citep{#1}}
\def\inparcite#1{\citealp{#1}}

@@

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking
or adequacy/fluency scales. However these provide no insight into the MT errors,
 and do not scale well with sentence 
length. We argue for a semantics-based evaluation, which aims to capture how much of the meaning
is retained in the MT output, and can support the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure for MT, Human
UCCA-based MT Evaluation (HUME), building on the Universal Conceptual Cognitive Annotation (UCCA) semantic representation scheme.
Making progress over previous work, the proposed measure takes into account
a wider range of semantic phenomena and does not rely on semantic annotation
of the MT output itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
as well as its reliability, reflected in its inter-annotator agreement rates.

@@

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}).
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments}) document the
efficiency (time of annotation) and inter-annotator agreement scores for HUME.
Finally, the differences with HMEANT are discussed 
(\secref{sec:hmeant_comp}).

@@

@@

%\subsection{Comparison with Crowdsourced Adequacy Judgements}\label{sec:adequacy}

@@

\bibliography{main}
\bibliographystyle{acl_natbib}

>>>>

\documentclass[11pt,letterpaper]{article}
%\usepackage[round]{natbib}
\usepackage{emnlp2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

\def\emnlppaperid{***}

@@

\def\perscite#1{\newcite{#1}}
\def\parcite#1{\cite{#1}}
\def\inparcite#1{\cite{#1}}

@@

Human evaluation of machine translation normally uses sentence-level measures such as relative ranking
or adequacy/fluency scales. However these provide no insight into the MT errors,
 and do not scale well with sentence 
length. We argue for a semantics-based evaluation, which aims to capture how much of the meaning
is retained in the MT output, and can support the construction and tuning of semantics-based MT. 
We present a novel human semantic evaluation measure for MT, Human
UCCA-based MT Evaluation (HUME), building on the Universal Conceptual Cognitive Annotation (UCCA) semantic representation scheme.
Making progress over previous work, the proposed measure takes into account
a wider range of semantic phenomena and does not rely on semantic annotation
of the MT output itself, whose interpretation is often unclear.
We experiment with four language pairs, demonstrating HUME's broad applicability,
as well as its reliability, reflected in its inter-annotator agreement rates and 
good correlation with human adequacy scores.

@@

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}).
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments}) document the
efficiency (time of annotation) and inter-annotator agreement scores for HUME. 
We also report on the correlation scores of HUME with direct assesment of human 
adequacy ratings. 
Finally, the differences with HMEANT are discussed 
(\secref{sec:hmeant_comp}).

@@

\subsection{Comparison with Crowdsourced Adequacy Judgements}\label{sec:adequacy}

\def\iaafig #1{\includegraphics[width=0.4\textwidth]{humevsDA_10en-#1.pdf}}

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{Plots of HUME scores vs Direct Assesment scores which have been standardised for each crowdsourcing annotator. The regression is calculated using linear least squares.}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{TODO} has proposed a new method for collecting 
accuracy ratings. The idea is that collecting a large number of adequacy judgements along a 
scale of 0 to 100 allows us to apply statistical measures which make them reliable. 
It has been shown that mean  judgements correlate very strongly with each other. 
We followed~\cite{TODO} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romainian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results. 
We can see that HUME and Direct Assesment scores do correlate. 
We also removed unreliable crowdsourcing annotators
according to the method discussed in ~\cite{TODO}. The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 which shows that they two measures do correlate. This confirms that 
the HUME metric is consistent with previously published methods in human evaluation, even though these
two approaches are very different in their conception.
We argue that although annotating HUME requires more expertise and effort, 
the results are more valuable because a HUME evaluation can tell you what parts
of the source sentence have been retained. Direct assesment scores require a crowd, which is sometimes not available or reliable, and it returns a single number which gives little insight into the quality of
the translated sentence.

@@

@@

\bibliography{main}
\bibliographystyle{emnlp2016}
